---
title: "Composite Index Construction"
output: 
  html_document: 
    code_folding: hide
    toc: true
    toc_float: true
    css: mystyle.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse=TRUE)
library(MASS)
library(ggplot2)
library(Amelia)
library(leaps)
library(MASS)
library(DMwR)
library(rgl)
```

## Brief Explanation 

An explanation of what indicators are and of the reason why they are widely used in companies and international organizations will be provided. The latest developments in methodology for the construction of indexes and indicators will be explained (economic activity, human development, poverty, finance, etc.). Special attention will be paid to their application in decision-making processes and, more precisely, to their usefulness in the context of forecasting. In particular, the methodology applied by international institutions in the construction of the most commonly known indexes will be explained, identifying and providing potential improvements. Students will solve a case study based on the real situation of an international institution using indicators.


## Introduction
A composite indicator measures multi-dimensional concepts (e.g. competitiveness, e-trade or environmental quality) which cannot be captured by a single indicator. Ideally, a composite indicator should be based on a theoretical framework / definition, which allows individual indicators / variables to be selected, combined and weighted in a manner which reflects the dimensions or structure of the phenomena being measure.

[EU VIDEO](https://www.youtube.com/watch?v=kz9g3d3xn6s)

## Some Examples

Some Composite Indicators:

-	Global AgeWatch Index. [GAWI.pdf](courseRBA_3/GAWI.pdf)
-	HDI. 
  [Link Wiki](https://en.wikipedia.org/wiki/Human_Development_Index)
  [EU VIDEO](https://www.youtube.com/watch?v=w5wORaWcWPY)
-	IQ
-	Economic Risk Indicator.
[Forecast.png](courseRBA_3/Forecast.png)


## Missing Value Imputation
```{r, warning=FALSE}
options(warn = -1)
#Import Data
path <- "courseRBA_3"
Data <- read.csv2(paste(path, "Income.csv", sep = "/"))
Data <- apply(Data, 2, as.numeric)

Data_estimate<-data.frame(Data)
x1<-Data_estimate[,1]
x2<-Data_estimate[,2]
x3<-Data_estimate[,3]
x4<-Data_estimate[,4]


#
dif<-matrix(0,length(x3),1)
dif2<-matrix(0,length(x3),1)
Data_estimate<-data.frame(Data_estimate)
leaps<-regsubsets(x3~x1+x2+x4,data=Data_estimate,nbest=2)
plot(leaps,scale="r2")
fit <- lm(x3~x1+x2+x4)
for (i in 1:length(x3)) {
  value_estimate=fit$coefficients[1]+fit$coefficients[2]*x2[i]+fit$coefficients[3]*x3[i]+fit$coefficients[4]*x4[i]
  dif[i]<-abs(x3[i]-value_estimate)/x3[i]
  }
check_value<-mean(dif[!is.na(dif)])
check_value2<-median(dif[!is.na(dif)])
check_value3<-sd(dif[!is.na(dif)])
print(check_value)
print(check_value2)
print(check_value3)
for (i in 1:length(x3)) {
  Data_estim<-Data
  Data_estim[i,3]<-NA
  Data_estimate<-data.frame(Data_estim)
  a.out <- amelia(Data_estimate, m = 1, boot.type = "none")
  unlist(a.out$imputations[[1]])
  em_estimation<-as.matrix(a.out$imputations[[1]])
  dif2[i]<-abs(x3[i]-em_estimation[i,3])/x3[i]
}
check_value<-mean(dif2[!is.na(dif2)])
check_value2<-median(dif2[!is.na(dif2)])
check_value3<-sd(dif2[!is.na(dif2)])
print(check_value)
print(check_value2)
print(check_value3)
Errors=cbind(dif,dif2)
ddf<-data.frame(Errors,GRP = c("Regression","EM"))
boxplot(Errors ~ GRP, main="Relative Welfare",data = ddf, lwd = 1, ylab = 'Errors')
stripchart(Errors~ GRP,vertical = TRUE, data = ddf, 
           method = "jitter", add = TRUE, pch = 20, col = c('blue','red'),cex=2)

```

## Outlier Detection
```{r, warning=FALSE}
Data_estimate<-data.frame(Data)
x1<-Data_estimate[,1]
x2<-Data_estimate[,2]
x3<-Data_estimate[,3]
x4<-Data_estimate[,4]
#Univariate
outlier_values <- boxplot.stats(x3)$out  # outlier values.
print(outlier_values)
boxplot(x3, boxwex=0.7)
mtext(paste("Outliers: None"), cex=1)
#Multivariate
#Cook DIstance
mod <- lm(x3 ~ ., data=Data_estimate)
cooksd <- cooks.distance(mod)
plot(cooksd, pch="*", cex=2, main="Influential Obs by Cooks distance")  # plot cook's distance
abline(h = 4*mean(cooksd, na.rm=T), col="red")  # add cutoff line
text(x=1:length(cooksd)+1, y=cooksd, labels=ifelse(cooksd>4*mean(cooksd, na.rm=T),names(cooksd),""), col="red")
#Mahalanobi Distance
Data2<-Data_estimate[,c(1:3)]
n.outliers   <- 2 # Mark as outliers the 2 most extreme points
m.dist.order <- order(mahalanobis(Data2, colMeans(Data2), cov(Data2)), decreasing=TRUE)
is.outlier   <- rep(FALSE, nrow(Data2))
is.outlier[m.dist.order[1:n.outliers]] <- TRUE
pch <- is.outlier * 16
col<- is.outlier + 1
plot3d(Data2[,1], Data2[,2], Data2[,3], type="s", col=col,xlab = "Pension",ylab="Poverty",zlab="Welfare")


```

## Normalization
```{r, warning=FALSE}

Data3<-Data
  for (i in 1:4) {
    Data3[,i]<-(Data3[,i]-min(Data3[,i]))/(max(Data3[,i])-min(Data3[,i]))
  }


Data4<-Data
for (i in 1:4) {
  Data4[,i]<-SoftMax( Data4[,i], lambda = 2, avg = mean( Data4[,i], na.rm = T), std = sd( Data4[,i], na.rm = T))
}

RR3<-cor(Data3)
check_value<-mean(dif[!is.na(dif2)])

RR<-cor(Data)
Data2<-Data
for (i in 1:4) {
  Data2[,i]<-scale(Data2[,i],TRUE,TRUE)
}

RR2<-cor(Data2)
dif<-RR-RR2
check_value<-mean(dif[!is.na(dif)])

RR4<-cor(Data4)
dif<-RR-RR4
check_value<-mean(dif[!is.na(dif)])


values<-matrix(0,4,3)
for (i in 1:4) {
par(mfrow=c(2,2))
hist(Data[,2], col=rgb(0.1,0,1,0.5),xlab="Original",main="Poverty Rate")
hist(Data2[,2], col=rgb(0.1,0,1,0.5),xlab="Standardization",main="Poverty Rate")
hist(Data3[,2], col=rgb(0.1,0,1,0.5),xlab="Max.Min",main="Poverty Rate")
hist(Data3[,2], col=rgb(0.1,0,1,0.5),xlab="SoftMax",main="Poverty Rate")

}
values<-matrix(values,42,1)
plot(values,ylim =c(0,0.00000001))

Max.Min<-matrix(0,99,1)
Original<-matrix(0,99,1)
softmax<-matrix(0,99,1)
z<-matrix(seq(0.01,0.99,0.01),99,1)
for ( i in c(1:99)) {
  Original[i]<-quantile(Data[,2],z[i])
  softmax[i]<-quantile(Data4[,2],z[i])
}



dat<-data.frame(Original,softmax)
ggplot(dat, aes(x=Original, y=softmax)) +
  geom_point(shape=5)      # Use hollow circles
ggplot(dat, aes(x=Original, y=softmax)) +
  geom_point(shape=1) +    # Use hollow circles
  geom_smooth(method=lm,level=0.9)  



```




