---
title: "Recommender Systems"
output:
  html_document: 
    code_folding: hide
    toc: true
    toc_float: true
    css: mystyle.css
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE
)
```

## Brief Explanation 

Almost every people has receipt a recommendation from them even if he/she has never heard about it.  Selling websites like Amazon or simple browsers as Google’s are training models from data in order to provide the best product or website to their customers given some information such as sociodemographic characteristics, historical purchased products or likes in websites. Obviously, recommender systems are on the spot of many companies and institutions who are trying to provide the most adequate item for a given person.  The concept and its typologies are motivated by illustrative examples obtained from recommender systems that are currently working. The final goal is to build a recommender systems from the scratch for a real problem.

This page contains a combination of traditional lecture materials (slides) and code demonstrating the relevant methods. The course will proceed by working through both. We will use several recent packages in our examples; see the [About](./About.html) page for information about the package versions.

```{r setup}
library(tidyverse)
library(grpreg)
library(splines)
library(refund)
library(refund.shiny)
```

## Practical example

In this section we will briefly examine implementations of variable selection methods, with emphasis on group variable selection methods using penalized approaches. The primary package and function is `grpreg::grpreg`; we'll start with the example included in the help file for this function.

A brief examination of the example data is below. Particular attention should be paid to variable classes.
```{r grpreg_BWT_explore, eval = TRUE}
data(Birthwt)
names(Birthwt)

class(Birthwt$X)
class(Birthwt$group)

head(Birthwt$X) %>% round(3)
Birthwt$group
```

Next we'll fit a regression for birthweight as a response and the grouped variables as predictors.
```{r grpreg_BWT_fit, eval = TRUE}
X <- Birthwt$X
group <- Birthwt$group
y <- Birthwt$bwt

fit_lasso <- grpreg(X, y, group, penalty="grLasso")
fit_MCP <- grpreg(X, y, group, penalty="grMCP")
fit_SCAD <- grpreg(X, y, group, penalty="grSCAD")

par(mfrow = c(1,3))
plot(fit_lasso)
plot(fit_MCP)
plot(fit_SCAD)
par(mfrow = c(1,1))
```

Examining coefficients at a few choices of the tuning parameter is also informative.
```{r grpreg_coefs, eval = TRUE}
fit_MCP$beta[,c(5,10,70)]
```

The `grpreg` package has two approaches for choosing the tuning parameter: selection using an information criterion and cross validation. The code below briefly compares these approaches using a Lasso penalty.
```{r grpreg_select, eval = TRUE}
coef_BIC = grpreg::select(fit_lasso, "BIC")$beta
coef_AIC = grpreg::select(fit_lasso, "AIC")$beta
fit_cv = cv.grpreg(X, y, group, penalty = "grLasso", seed = 1)
coef_CV = fit_cv$fit$beta[,fit_cv$min]

cbind(coef_BIC, coef_AIC, coef_CV)
```


## Try it yourself!

Next we'll take a few minutes for some independent coding. Using the DTI dataset, create predictors based on averaging across profiles. Grouping these within tracts (or within modalities), use these as predictors of _pasat_ or _case_.

```{r grpreg_DTI, eval = FALSE, echo = FALSE}
load("./DataCode/DTI.RDA")

predictor_names = paste(rep(c("CSTR", "CSTL", "CCA", "OPRL", "OPRR"), each = 6), 
									rep(c("ani", "l0", "lt", "md", "mtr", "t2"), 5), 
									sep = "_")
tract_means = map(predictor_names, ~apply(get(.x), 1, mean, na.rm = TRUE))

X = matrix(unlist(tract_means), 211, 30, byrow = FALSE)
y = outcome_data$pasat

keep = complete.cases(cbind(y, X))
X = X[keep,]
y = y[keep]

group = factor(rep(c("CSTR", "CSTL", "CCA", "OPRL", "OPRR"), each = 6), 
               levels = c("CSTR", "CSTL", "CCA", "OPRL", "OPRR"))

fit_lasso <- grpreg(X, y, group, penalty="grLasso")
fit_MCP <- grpreg(X, y, group, penalty="grMCP")
fit_SCAD <- grpreg(X, y, group, penalty="grSCAD")

par(mfrow = c(1,3))
plot(fit_lasso)
plot(fit_MCP)
plot(fit_SCAD)
par(mfrow = c(1,1))

coef_BIC = grpreg::select(fit_lasso, "BIC")$beta
coef_AIC = grpreg::select(fit_lasso, "AIC")$beta
fit_cv = cv.grpreg(X, y, group, penalty = "grLasso", seed = 1)
coef_CV = fit_cv$fit$beta[,fit_cv$min]

cbind(coef_BIC, coef_AIC, coef_CV)
```
